---
title: "Gail Score Prediction Based on Facebook"
output: pdf_document
---

The following chunk is for installing and loading all the required packages.
```{r}
install.packages("stringr", dependencies = T)
install.packages("Rfacebook", dependencies = T)
install.packages("genderdata", dependencies = T)
install.packages("gender", dependencies = T)
install.packages("wru", dependencies = T)
install.packages("foreach", dependencies = T)
install.packages("doParallel", dependencies = T)
install.packages("coda", dependencies = T)
install.packages("BCRA", dependencies = T)
library(stringr)
library(Rfacebook)
library(gender)
library(wru)
library(foreach)
library(doParallel)
library(coda)
library(BCRA)
library(knitr)
```
# Getting the data from facebook.
The following first chunk of code should be run separately due to interactive environment. I have commented it out from the rest of the code. I have added a separate folder for which contains the .r file for this chunk which can be run to get the data. I have stored the data and for the rest of the code I am reading from it. It runs in the following way.
After the code is run, press enter in the R console. After that the an authentication page will be opened in a browser which is then closed. Then the chunk of codes after this is implemented(can implement all the rest at a time).
The following chunk creates a token to get information from other pages. First I create API account linked to my facebook account which gives an id which is used to create the token. 
```{r}
#fb_oauth <- fbOAuth(app_id = "1286708611360084", 
#app_secret = "c5a2e978bb2b0425f0d02990ae60f9db", #extended_permissions = TRUE)
```

```{r}
# page <- getPage(page="thebreastcancersite", token=fb_oauth, n = 1000, 
# since='2016/09/15', until='2016/09/16')
# post_id <- which(page$id == "7210086721_10153795081091722")
# post <- getPost(post= page$id[post_id], n=2000, token=fb_oauth)
# comments <- post$comments
# #-- Cant have access to 241 user ---#
# comments_users_info <- getUsers(comments$from_id[-241], token=fb_oauth)
# unique_comments_users_info <- comments_users_info[!duplicated(comments_users_info$id), ]
# 
# length_unique <- nrow(unique_comments_users_info)
# access_comments <- comments[-241,]
# trim_access_comments <- access_comments$message[1: length_unique]
# comments_users_info_append_comments 
# <- cbind(unique_comments_users_info, trim_access_comments)
# names_first <- comments_users_info_append_comments$first_name
```

In the following chunk of code, gender is predicted for all the users that I get from the above data and only the female users are extracted.
```{r}
# #--- Identifying which are females--#
# 
# check_genderdata_package()
# #1
# which_females <- c()
# for(i in 1 : length(names_first))
# {
#   f <- gender(names_first[i], method = "ssa")
#   if(length(f$gender) != 0 && f$gender == "female")
#   {
#     which_females <- c(which_females, i)      
#   }
#   
#   
#   #print(i)
# }
# female_users <- comments_users_info_append_comments[which_females,]
# 
# colnames(female_users)[12] <- c("comments")
# fb_data <- female_users[c(1,2,4,6,11,12)]
# colnames(fb_data) <- c("fb_id","name","first_name","last_name","picture_url","comments")
# saveRDS(fb_data,file="fb_data.Rda")
```

```{r}
start.time <- Sys.time()
```


## Processing the data.

The last line of the above chunk saves the data which is the same data given in the data folder. Now the data is read into R and presence of medical history is detected by looking into some key words like breast cancer, diagnosed,..
```{r, warning=FALSE}
fb_data <- readRDS(file = "fb_data.Rda")
comments_fb <- fb_data$comments
md_hist <- rep(0, length(comments_fb))
biopsy <- rep(0, length(comments_fb))
for(i in 1 : length(comments_fb))
{
  #c1 <- grep("Breast", comments_fb[i], ignore.case = T)
  c2 <- grep("Survivor", comments_fb[i], ignore.case = T)
  c3 <- grep("Free", comments_fb[i], ignore.case = T)
  c4 <- grep("Diagnosed", comments_fb[i], ignore.case = T)
  c5 <- grep("Diagnosis", comments_fb[i], ignore.case = T)
  c6 <- grep("Cancer", comments_fb[i], ignore.case = T)
  c7 <- grep("Lung", comments_fb[i], ignore.case = T)
  c8 <- grep("Masectomy", comments_fb[i], ignore.case = T)
  c9 <- grep("Lumpectomy", comments_fb[i], ignore.case = T)
  c10 <- grep("Biopsy", comments_fb[i], ignore.case = T)
  c11 <- grep("Biopsies", comments_fb[i], ignore.case = T)
  #k <- length(c2) + length(c3) + length(c4) + length(c5)
  #print(k)
  if(length(c2) + length(c3) + length(c4) + length(c5) + length(c6) >= 1)
    md_hist[i] = 1
  else
    md_hist[i] = 0

  if(length(c7) == 1)
    md_hist[i] = 0
  if(length(c8) + length(c9) + length(c10) >= 1)
    biopsy[i] = 1
  else
    biopsy[i] = 0
}
processed_data <- cbind(fb_data, md_hist, biopsy)
colnames(processed_data)[7:8] <- c("Medical_History", "Biopsy")
#head(processed_data)
```

# Method

The following chunk determines the age from the first name of a person using the name-age calculator data which gives the 25th quantile, median and 75th quantile.

```{r, warning=FALSE}
h <- as.character(processed_data$first_name)
#print(h)
h <- paste0(h,"-")
name_age_calc <- function(x)
{
  index <- which(str_detect(list.files(pattern = "-stats.txt$", recursive = TRUE),x) 
                 == TRUE)
  if(length(index) != 0)
  {
    d <- read.table(list.files(pattern = "-stats.txt$", recursive = TRUE)[index],
                    header = F)
    g <- as.character(d[2,])
    return(c(as.numeric(str_sub(g,6,9)), 
             as.numeric(str_sub(g,1,4)), as.numeric(str_sub(g,11,14))))
  }

  else
    return(c(0,0,0))

}
no_cores <- detectCores() - 1
cl <- makeCluster(no_cores)
registerDoParallel(cl)
name_age_list <- foreach(i = 1:length(h), .packages = c("stringr")) %dopar%
  name_age_calc(h[i])
stopCluster(cl)

m <- do.call(rbind, name_age_list)
m <- as.data.frame(m)
colnames(m) <- c("25percentile","Median","75percentile")
data1 <- cbind(processed_data, m)
lowlimit_age <- 2015 - data1[,11]
uplimit_age <- 2015 - data1[,9]
median_age <- 2015 - data1[,10]
data1 <- cbind(data1, lowlimit_age, uplimit_age, median_age)

colnames(data1)[12:14] <- c("Lower_age", "Upper_age", "Median_age")
data1 <- data1[which(data1$Lower_age >= 35 & data1$Upper_age <= 90 &
                       data1$Upper_age != 2015 & data1$Medical_History == 0),]
#head(data1)
```

This chunk of code predicts the race from the surnames using the wru package which uses social security data. 1 denotes white, 2 denotes black, 3 for hispanic and 11 for asians.
```{r}
# #-- Identifying race based on surnames --#
female_surnames <- as.data.frame(data1$last_name)
colnames(female_surnames) <- c("surname")
race_prediction <- race.pred(voters = female_surnames, 
                             races = c("white", "black", "latino", "asian", "other"),
                             surname.only = TRUE)
target <- female_surnames$surname

order_r_p <- race_prediction[match(target,race_prediction$surname),]

order_r_p_without_surnames <- order_r_p[,-1]
race <- c()
for(i in 1 : nrow(order_r_p))
{
  if(which(order_r_p_without_surnames[i,] == max(order_r_p_without_surnames[i,])) == 1)
    race <- c(race,"White")
  if(which(order_r_p_without_surnames[i,] == max(order_r_p_without_surnames[i,])) == 2)
    race <- c(race,"Black")
  if(which(order_r_p_without_surnames[i,] == max(order_r_p_without_surnames[i,])) == 3)
    race <- c(race,"Hispanic")
  if(which(order_r_p_without_surnames[i,] == max(order_r_p_without_surnames[i,])) == 4)
    race <- c(race,"Asian")
  if(which(order_r_p_without_surnames[i,] == max(order_r_p_without_surnames[i,])) == 5)
    race <- c(race,"Others")
}
data1 <- cbind(data1,race)
colnames(data1)[15] <- c("Race")
code_fun <- function(x)
{
  if(x == "White")
    return(1)
  if(x == "Black")
    return(2)
  if(x == "Hispanic")
    return(3)
  if(x == "Asian")
    return(11)
}
Race <- apply(as.data.frame(data1$Race), 1, code_fun)
data1$Race <- Race
```

In this chunk of code different races are predicted with different posterior probabilities and only those are taken whose is > 0.1%. Estimates the absolute risk for five years as well as the lifetime risk for the median age and most probable race using Gail model. Also estimates the same for different probable ages and races to get the uncertainity.
```{r}
#---- Range of Race-------
race_high_prob <- function(x)
{
  return(which(as.matrix(x) > 0.001))
}
Race_individual <- apply(as.matrix(order_r_p[,-1]), 1, race_high_prob)

race_code <- function(x)
{
  if(length(which(x == 4)) > 0)
   x[which(x == 4)] = 11
  if(length(which(x == 5)) > 0)
    x = x[-which(x == 5)]
  return(x)
}

Race_code_individual <- lapply(Race_individual, race_code)

ID <- seq(1, nrow(data1), 1)
T1 <- data1$Median_age
T2_90 <- rep(90, nrow(data1))
T2_5 <- T1 + 5
T2_5 <- ifelse(T2_5 <= 90, T2_5, 90)
N_Biop <- rep(99, nrow(data1))
HypPlas <- rep(99, nrow(data1))
AgeMen <- rep(99, nrow(data1))
Age1st <- rep(99, nrow(data1))
N_Rels <- rep(99, nrow(data1))
mp_race <- data1$Race
Individual_5 <- cbind(ID, T1, T2_5, N_Biop, HypPlas, AgeMen, Age1st, N_Rels, mp_race)
colnames(Individual_5) <- c("ID", "T1", "T2", "N_Biop", "HypPlas", "AgeMen", "Age1st", 
                            "N_Rels", "Race")
Individual_90 <- cbind(ID, T1, T2_90, N_Biop, HypPlas, AgeMen, Age1st, N_Rels, mp_race)
colnames(Individual_90) <- c("ID", "T1", "T2", "N_Biop", "HypPlas", "AgeMen", "Age1st", 
                            "N_Rels", "Race")
no_cores <- detectCores() - 1
# Initiate cluster
cl <- makeCluster(no_cores)
registerDoParallel(cl)
Est_absolute_fiveyear_risk_ma_mpr <- foreach(i = 1:nrow(data1),.packages = ("BCRA"))%dopar%
absolute.risk(as.data.frame(t(Individual_5[i,])), iloop = 1)
Est_absolute_lifetime_risk_ma_mpr <- foreach(i = 1:nrow(data1),.packages = ("BCRA"))%dopar%
absolute.risk(as.data.frame(t(Individual_90[i,])), iloop = 1)
stopCluster(cl)
#Est_absolute_fiveyear_risk_ma_mpr_unlist <- do.call(rbind, Est_absolute_fiveyear_risk_ma_mpr)
#Est_absolute_lifetime_risk_ma_mpr_unlist <- do.call(rbind, Est_absolute_lifetime_risk_ma_mpr)
Est_score <- as.data.frame(cbind(data1$name, data1$Median_age, data1$Race, 
                                 as.numeric(Est_absolute_fiveyear_risk_ma_mpr), 
                                 Aas.numeric(Est_absolute_lifetime_risk_ma_mpr)))
colnames(Est_score) <- c("Name", "Median_age", "Most_probable race", "Gail_score", "Lifetime risk")
```
# Results

The estimated absolute risk and lifetime risk for some of the women are:
```{r}
head(Est_score)
```

There are no women in this data set whose estimated gail score is greater than 1.66.
```{r}
#Est_gail_score <- as.data.frame(cbind(data1$name, data1$Median_age, data1$Race,
                                  
  #                                    as.numeric(Est_absolute_fiveyear_risk_ma_mpr)))
#colnames(Est_gail_score) <- c("Name", "Median_age", "Most_probable race", "Gail_score")
High_risk_individuals <- Est_score[which(as.numeric(Est_absolute_fiveyear_risk_ma_mpr) >= 1.66),]
print(nrow(High_risk_individuals))
Individual_age <- list()
for(i in 1: nrow(data1))
{
  Range_age <- seq(data1$Lower_age[i], data1$Upper_age[i],1)
  m <- matrix(0, nrow = length(Range_age), ncol = 5)
  ID <- seq(1, length(Range_age),1)
  T2_90 <- rep(90, length(Range_age))
  T2_5 <- Range_age + 5
  T2_5 <- ifelse(T2_5 <= 90, T2_5, 90)
  N_Biop <- rep(99, length(Range_age))
  HypPlas <- rep(99, length(Range_age))
  AgeMen <- rep(99, length(Range_age))
  Age1st <- rep(99, length(Range_age))
  N_Rels <- rep(99, length(Range_age))
  race_i <- rep(data1$Race[i],length(Range_age) )
  final_data_five <- as.data.frame(cbind(ID, Range_age, T2_5, N_Biop, HypPlas,
                                         AgeMen, Age1st, N_Rels, race_i))
  colnames(final_data_five) <- c("ID", "T1", "T2", "N_Biop", "HypPlas", 
                                 "AgeMen", "Age1st", "N_Rels", "Race")
  final_data_ninety <- as.data.frame(cbind(ID, Range_age, T2_90, N_Biop, HypPlas,
                                           AgeMen, Age1st, N_Rels, race_i))
  colnames(final_data_ninety) <- c("ID", "T1", "T2", "N_Biop", "HypPlas",
                                   "AgeMen", "Age1st", "N_Rels", "Race")
  Abs_risk_i_five <- absolute.risk(final_data_five, iloop = 1)
  Abs_avg_risk_i_five <- absolute.risk(final_data_five, iloop = 2)
  Abs_risk_i_ninety <- absolute.risk(final_data_ninety, iloop = 1)
  Abs_avg_risk_i_ninety <- absolute.risk(final_data_ninety, iloop = 2)
  m[,1] <- Abs_risk_i_five
  m[,2] <- Abs_avg_risk_i_five
  m[,3] <- Abs_risk_i_ninety
  m[,4] <- Abs_avg_risk_i_ninety
  m[,5] <- Range_age
  Individual_age[[i]] <- m
}

list_matrix_age <- do.call(rbind, Individual_age)
min_max_age <- c(min(list_matrix_age[,1]), min(list_matrix_age[,2]),
                 min(list_matrix_age[,3]), min(list_matrix_age[,4]), 
                 max(list_matrix_age[,1]), max(list_matrix_age[,2]),
             max(list_matrix_age[,3]), max(list_matrix_age[,4]))


x_names <- c("Absolute risk(5 years)","Average absolute risk(5 years)",
             "Lifetime absolute risk","Average lifetime risk")
age_min <- min(list_matrix_age[,5])
age_max <- max(list_matrix_age[,5])
```



This plot shows how the absolute risk for five years and varies with age with their race fixed at the most probable race.
```{r}

  #pdf(paste0("pic_", j, ".pdf"))
  par(mfrow = c(2,2))
  for(i in 1 :4)
  {
    median_abs_risk_age <- which(Individual_age[[i]][,5] == data1$Median_age[i] )
    plot(Individual_age[[i]][,5], Individual_age[[i]][,1], 
         main = paste(data1$first_name[i]), 
         ylab = paste(x_names[1]), xlab = "Age", type = "l", col = "red",
         ylim = c(min_max_age[1],min_max_age[1+4]))
    points(data1$Median_age[i], Individual_age[[i]][median_abs_risk_age,1],
           
           col = "blue", pch = 16 )
    legend("topright", paste("Median age"), 
           col = c("blue"),
           pch = 16, bty = "n")
  }
```

This plot shows how the lifetime risk varies with age with their race fixed at the most probable race.
```{r}
par(mfrow = c(2,2))
  for(i in 1 :4)
  {
    median_abs_risk_age <- which(Individual_age[[i]][,5] == data1$Median_age[i] )
    plot(Individual_age[[i]][,5], Individual_age[[i]][,3], 
         main = paste(data1$first_name[i]), ylab = paste(x_names[3]), xlab = "Age", 
         type = "l", 
         col = "red",
         ylim = c(min_max_age[3],min_max_age[3+4]))
    points(data1$Median_age[i], Individual_age[[i]][median_abs_risk_age,3], col = "blue",
           pch = 16 )
    legend("topright", paste("Median age"), 
           col = c("blue"),
           pch = 16, bty = "n")
  }

```



```{r}
 Individual_race <- list()
 for(i in 1: nrow(data1))
 {
   Range_race <- Race_code_individual[[i]]
   age_i <- rep(data1$Median_age[i],length(Range_race))
   m <- matrix(0, nrow = length(Range_race), ncol = 5)
   ID <- seq(1, length(Range_race),1)
   T2_90 <- rep(90, length(Range_race))
   T2_5 <- age_i + 5
   T2_5 <- ifelse(T2_5 <= 90, T2_5, 90)
   N_Biop <- rep(99, length(Range_race))
   HypPlas <- rep(99, length(Range_race))
   AgeMen <- rep(99, length(Range_race))
   Age1st <- rep(99, length(Range_race))
   N_Rels <- rep(99, length(Range_race))
   final_data_five <- as.data.frame(cbind(ID, age_i, T2_5, N_Biop, HypPlas, 
                                          AgeMen, Age1st, N_Rels, Range_race))
   colnames(final_data_five) <- c("ID", "T1", "T2", "N_Biop", "HypPlas", 
                                  "AgeMen", "Age1st", "N_Rels", "Race")
   final_data_ninety <- as.data.frame(cbind(ID, age_i, T2_90, N_Biop, HypPlas, 
                                            AgeMen, Age1st, N_Rels, Range_race))
   colnames(final_data_ninety) <- c("ID", "T1", "T2", "N_Biop", "HypPlas", 
                                    "AgeMen", "Age1st", "N_Rels", "Race")
   Abs_risk_i_five <- absolute.risk(final_data_five, iloop = 1)
   Abs_avg_risk_i_five <- absolute.risk(final_data_five, iloop = 2)
   Abs_risk_i_ninety <- absolute.risk(final_data_ninety, iloop = 1)
   Abs_avg_risk_i_ninety <- absolute.risk(final_data_ninety, iloop = 2)
   m[,1] <- Abs_risk_i_five
   m[,2] <- Abs_avg_risk_i_five
   m[,3] <- Abs_risk_i_ninety
   m[,4] <- Abs_avg_risk_i_ninety
   m[,5] <- Range_race
   Individual_race[[i]] <- m
 }

 list_matrix_race <- do.call(rbind, Individual_race)
 min_max_race <- c(min(list_matrix_race[,1]), min(list_matrix_race[,2]), min(list_matrix_race[,3]),    min(list_matrix_race[,4]), max(list_matrix_race[,1]), max(list_matrix_race[,2]),
              max(list_matrix_race[,3]), max(list_matrix_race[,4]))
```

This plot shows how the absolute risk for five years varies with race with their age fixed at the median age.
```{r}
   par(mfrow = c(2,2))
   for(i in 1 :4)
   {
     most_probable_race <- which(Individual_race[[i]][,5] == data1$Race[i] )
     plot(Individual_race[[i]][,5], Individual_race[[i]][,1], main = paste(data1$first_name[i]),
          ylab = paste(x_names[1]), 
          xlab = "Race: 1-Wh, 2-Bl, 3-His and 11-Asi", 
          col = "red", pch = 16,
          ylim = c(min_max_race[1],min_max_race[1+4]))
     points(data1$Race[i], Individual_race[[i]][most_probable_race,1], col = "blue", pch = 16)
     legend("topright", paste("Most probable race"), col = c("blue"),
            pch = 16)
   }
```

This plot shows how the lifetime risk varies with race with their age fixed at the median age.
```{r}
par(mfrow = c(2,2))
  for(i in 1 :4)
  {
    most_probable_race <- which(Individual_race[[i]][,5] == data1$Race[i] )
    plot(Individual_race[[i]][,5], Individual_race[[i]][,3], main = paste(data1$first_name[i]),
         ylab = paste(x_names[3]), 
         xlab = "Race: 1-Wh, 2-Bl, 3-His and 11-Asi", 
         col = "red", pch = 16,
         ylim = c(min_max_race[3],min_max_race[3+4]))
    points(data1$Race[i], Individual_race[[i]][most_probable_race,3], col = "blue", pch = 16)
    legend("topright", paste("Most probable race"), col = c("blue"),
           pch = 16)
  }
dev.off()
```



```{r}
Individual_age_race_5 <- list()
for(i in 1: nrow(data1))
{
  Range_race <- Race_code_individual[[i]]
  Range_age <- seq(data1$Lower_age[i], data1$Upper_age[i],1)
  Range_age_race <- expand.grid(Range_age, Range_race)
  colnames(Range_age_race) <- c("Age", "Race")
  T1 <- Range_age_race$Age
  R <- Range_age_race$Race
  m <- matrix(0, nrow = nrow(Range_age_race), ncol = 6)
  ID <- seq(1, nrow(Range_age_race), 1)
  T2_5 <- T1 + 5
  T2_5 <- ifelse(T2_5 <= 90, T2_5, 90)
  N_Biop <- rep(99, nrow(Range_age_race))
  HypPlas <- rep(99, nrow(Range_age_race))
  AgeMen <- rep(99, nrow(Range_age_race))
  Age1st <- rep(99, length(Range_race))
  N_Rels <- rep(99, nrow(Range_age_race))
  final_data_five <- as.data.frame(cbind(ID, T1, T2_5, N_Biop, HypPlas, 
                                         AgeMen, Age1st, N_Rels, R))
  colnames(final_data_five) <- c("ID", "T1", "T2", "N_Biop", "HypPlas", "AgeMen",
                                 "Age1st", "N_Rels", "Race")
  Individual_age_race_5[[i]] <- final_data_five
}

Individual_age_race_90 <- list()
for(i in 1: nrow(data1))
{
  Range_race <- Race_code_individual[[i]]
  Range_age <- seq(data1$Lower_age[i], data1$Upper_age[i],1)
  Range_age_race <- expand.grid(Range_age, Range_race)
  colnames(Range_age_race) <- c("Age", "Race")
  T1 <- Range_age_race$Age
  R <- Range_age_race$Race
  m <- matrix(0, nrow = nrow(Range_age_race), ncol = 6)
  ID <- seq(1, nrow(Range_age_race), 1)
  T2_90 <- rep(90, nrow(Range_age_race))
  N_Biop <- rep(99, nrow(Range_age_race))
  HypPlas <- rep(99, nrow(Range_age_race))
  AgeMen <- rep(99, nrow(Range_age_race))
  Age1st <- rep(99, length(Range_race))
  N_Rels <- rep(99, nrow(Range_age_race))
  final_data_ninety <- as.data.frame(cbind(ID, T1, T2_90, N_Biop, HypPlas,
                                           AgeMen, Age1st, N_Rels, R))
  colnames(final_data_ninety) <- c("ID", "T1", "T2", "N_Biop", "HypPlas",
                                   "AgeMen", "Age1st", "N_Rels", "Race")
  Individual_age_race_90[[i]] <- final_data_ninety
}
# Calculate the number of cores
no_cores <- detectCores() - 1
# Initiate cluster
cl <- makeCluster(no_cores)
registerDoParallel(cl)
n <- length(Individual_age_race_5)
Est_absolute_fiveyear_risk <- foreach(i = 1:n,.packages = ("BCRA")) %dopar%
  absolute.risk(Individual_age_race_5[[i]], iloop = 1)
Est_avg_absolute_fiveyear_risk <- foreach(i = 1:n,.packages = ("BCRA")) %dopar%
  absolute.risk(Individual_age_race_5[[i]], iloop = 2)
Est_absolute_lifetime_risk <- foreach(i = 1:n,.packages = ("BCRA")) %dopar%
  absolute.risk(Individual_age_race_90[[i]], iloop = 1)
Est_avg_absolute_lifetime_risk <- foreach(i = 1:n,.packages = ("BCRA")) %dopar%
  absolute.risk(Individual_age_race_90[[i]], iloop = 2)
stopCluster(cl)
```

Calculating 2.5 and 97.5 empirical quantiles for uncertainity.
```{r}
quant <- function(x)
{ return(quantile(x, probs = c(0.025, 0.975)))}

hpd <- function(x)
{
  HPDinterval(as.mcmc(x), prob=0.95)
}

quant_absolute_fiveyear_risk <- lapply(Est_absolute_fiveyear_risk, quant)
quant_avg_absolute_fiveyear_risk <- lapply(Est_avg_absolute_fiveyear_risk, quant)
quant_absolute_lifetime_risk <- lapply(Est_absolute_lifetime_risk, quant)
quant_avg_absolute_lifetime_risk <- lapply(Est_avg_absolute_lifetime_risk, quant)


# hpd_absolute_fiveyear_risk <- lapply(Est_absolute_fiveyear_risk, hpd)
# hpd_avg_absolute_fiveyear_risk <- lapply(Est_avg_absolute_fiveyear_risk, hpd)
# hpd_absolute_lifetime_risk <- lapply(Est_absolute_lifetime_risk, hpd)
# hpd_avg_absolute_lifetime_risk <- lapply(Est_avg_absolute_lifetime_risk, hpd)


list_matrix_quant_absolute_fiveyear_risk <- do.call(rbind, quant_absolute_fiveyear_risk)
list_matrix_quant_avg_absolute_fiveyear_risk <- do.call(rbind,
  quant_avg_absolute_fiveyear_risk)
list_matrix_quant_absolute_lifetime_risk <- do.call(rbind, quant_absolute_lifetime_risk)
list_matrix_quant_avg_absolute_lifetime_risk <- do.call(rbind, 
                                                        quant_avg_absolute_lifetime_risk)

# list_matrix_hpd_absolute_fiveyear_risk <- do.call(rbind, hpd_absolute_fiveyear_risk)
# list_matrix_hpd_avg_absolute_fiveyear_risk <- do.call(rbind, hpd_avg_absolute_fiveyear_risk)
# list_matrix_hpd_absolute_lifetime_risk <- do.call(rbind, hpd_absolute_lifetime_risk)
# list_matrix_hpd_avg_absolute_lifetime_risk <- do.call(rbind, hpd_avg_absolute_lifetime_risk)
full_names <- as.character(data1$name)

Confidence_Interval <- as.data.frame(cbind(full_names,
                                           list_matrix_quant_absolute_fiveyear_risk, list_matrix_quant_avg_absolute_fiveyear_risk, list_matrix_quant_absolute_lifetime_risk, 
                                           list_matrix_quant_avg_absolute_lifetime_risk))
# HPD_Confidence_Interval <- as.data.frame(cbind(full_names,list_matrix_hpd_absolute_fiveyear_risk, list_matrix_hpd_avg_absolute_fiveyear_risk, list_matrix_hpd_absolute_lifetime_risk, list_matrix_hpd_avg_absolute_lifetime_risk))
```

The second and third columns are for the absolute risk whereas six and seven columns are for the lifetime risk.
```{r}
head(Confidence_Interval)
```

```{r}
end.time <- Sys.time()
```

Total time elapsed for the above code
```{r}
end.time - start.time
```


